Intrusion Detection with Genetic Algorithms and Fuzzy Logic

### 2013-09-26 annotated_bibliography.tex
Worked on my annotated bibliography.

\title{Something about NP-complete problems}

@@

\begin{abstract}
This paper discusses new results in NP-complete problems and the use of distributed
networks to solve certain partial cases of NP-complete problems.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Delphi theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

\section{Introduction}
I will focus on using the approach Blah for solving partial cases of
NP-complete problems on distributed networks.

I plan to use the following sources:
\begin{itemize}
\item I expect~\cite{OM:2008} to be one of my main sources, and I'm still looking for another two ``core'' papers to build on.
\item I may use~\cite{Brun:2008} for comparison. 
\item I'll use~\cite{Aaronson:2005, wiki:np-complete} and possibly selected chapters of~\cite{Garey:1979} as background. 
\end{itemize}

As mentioned above I need two other ``core'' papers, and I'm still looking for good examples that I can use to explain the

I was initially considering algorithms on compete graphs as a possible topic, and looked over~\cite{winkler1984isometric, dobkin1987delaunay, folkman1970graphs} before I settled on my current topic.

>>>>

\title{Intrusion Detection with Genetic Algorithms and Fuzzy Logic}

@@

\begin{abstract}
This paper discusses the use of artificial intelligence in intrusion detection systems.
\end{abstract}

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Intrusion detection}

\keywords{Genetic algorithms, Fuzzy logic}

\section{Introduction}
I will be looking at how genetic algorithms and fuzzy logic are used to train intrusion detection systems about possible threats.

I plan to use the following sources:
\begin{itemize}
\item I expect~\cite{DBLP:journals/corr/abs-1204-1336} and~\cite{6496342} to be two of my main sources.
\item I may use~\cite{bc1_ecindm} for my third source or for background. 
\item I'll use~\cite{Liao201316, DBLP:journals/corr/abs-1204-6416, bapuji2012soft} as background. 
\end{itemize}

I won't be using~\cite{Sangkatsanee20112227}, because it doesn't talk about genetic algorithms or fuzzy logic.
